\textbf{ Normalized Gaussian Processes }

### 2020-11-25 tex/ms.tex
more nbs
better:

Let $\mathbf{x} = \left( x_0 \,\, \cdots \,\, x_{K-1} \right)^\top$
be a $K$-dimensional multivariate normal random variable distributed
according to a Gaussian Process with mean $\pmb{\mu}$
and covariance $\pmb{\Sigma}$:
%
\begin{align}
    \mathbf{x} \sim \mathcal{N}\left( \pmb{\mu}, \pmb{\Sigma} \right)
    \quad.
\end{align}
%
For simplicity, let us assume the mean is constant, i.e.,
%
\begin{align}
    \pmb{\mu} = \mu \, \mathbf{j}_K
\end{align}
%
where $\mathbf{j}_K$ is the vector of $K$ ones.
%
Now suppose we cannot observe samples of $\mathbf{x}$ directly, but instead we can
observe samples from the \emph{normalized} process, which we will call
$\tilde{\mathbf{x}}$:
%
\begin{align}
    \tilde{\mathbf{x}}
     & \equiv \frac{\mathbf{x}}{\bar{x}}
    \nonumber                                                      \\[0.5em]
     & = \frac{\mathbf{x}}{\frac{1}{K}\sum\limits_{k=0}^{K-1} x_k}
    \quad.
\end{align}
%
The random variable $\tilde{\mathbf{x}}$ is no longer normally distributed, but as long as
the variance of $\bar{x}$ is small, we can approximate it as such. Let the mean
and covariance of $\tilde{\mathbf{x}}$ be $\tilde{\pmb{\mu}}$ and $\tilde{\pmb{\Sigma}}$, respectively:
%
\begin{align}
    \tilde{\mathbf{x}} \mathrel{\dot\sim} \mathcal{N}\left( \tilde{\pmb{\mu}}, \tilde{\pmb{\Sigma}} \right)
    \quad.
\end{align}
%
By definition, the mean is unity, i.e,
%
\begin{align}
    \tilde{\pmb{\mu}} = \mathbf{j}_K
    \quad.
\end{align}
%
What is the expression for $\tilde{\pmb{\Sigma}}$?

@@

        \left(\frac{\mathbf{x}}{\bar{x}} - \mathbf{j}_K\right)
        \left(\frac{\mathbf{x}}{\bar{x}} - \mathbf{j}_K\right)^\top

@@

        \frac{\mathbf{x}\,\mathbf{j}_K^\top}{\bar{x}}

@@

        \frac{\mathbf{j}\,\mathbf{x}_K^\top}{\bar{x}}

@@

        \mathbf{J}_K

@@

        \frac{\mathbf{j}_K\,\mathbf{x}^\top}{\bar{x}}

@@

where $\mathbf{J}_K = \mathbf{j}_K \mathbf{j}_K^\top$ is the $K\times K$ matrix of ones.

@@

    \mathbf{u} \sim \mathcal{N}\left( 0, \mathbf{I}_K \right)

@@

where $\mathbf{I}_K$ is the

@@

            (\pmb{\mu} + \mathbf{L} \mathbf{u})\mathbf{j}_K^\top

@@

            \mathbf{j}_K(\pmb{\mu} + \mathbf{L} \mathbf{u})^\top

@@

    \mu + \frac{1}{K}\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}

@@

    z \equiv \frac{1}{\mu K}\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}

@@

        \frac{z^2 \, \mathbf{J}_K}{(1 + z)^2}

@@

        \frac{z\, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top}{(1 + z)^2}

@@

intractable. As long as
$\big|z| < 1$, we can Taylor expand the matrices as

@@

        \mathbf{j}_K^\top

@@

In the Appendix, we show that these may be computed from

@@

        z^{n + 2} \, \mathbf{J}_K

@@

    (n + 1) g_{n} \, \bar{\Sigma}^\frac{n+2}{2} \, \mathbf{J}_K

@@

        z^{n + 1} \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top

@@

    (n + 1) K \, g_{n} \, \mathbf{S}^\frac{n+2}{2}

@@

    n \, g_{n} \, \mathbf{S}^\frac{n}{2}\pmb{\Sigma} + g_{n} \, \bar{\Sigma}^\frac{n}{2} \pmb{\Sigma}

@@

@@

@@

    \mathbf{S}

@@

    \frac{1}{K^2} \pmb{\Sigma} \, \mathbf{J}_K

@@

and $\bar{\Sigma}$ is the average of all the elements in $\pmb{\Sigma}$.

@@

Inserting these expressions into Equation~(\ref{eq:SigmaPQR}), we obtain

@@

    \resizebox{.85\hsize}{!}{$
            (-1)^n (n + 1)^2 g_n
            \bar{\Sigma}^\frac{n+2}{2} \mathbf{J}_K
            \frac{K}{\mu}\left( \mathbf{S}^\frac{n+2}{2} + {\mathbf{S}^\top}^\frac{n+2}{2} \right)
            \frac{n}{(n+1)\mu^2}
            \mathbf{S}^\frac{n}{2} \mathbf{\Sigma}
            \bar{\Sigma}^\frac{n}{2} \mathbf{I}_K
            \mathbf{\Sigma}
        $}

@@

The convergence criterion for this series may be written

@@

    \mathbb{E}\big[|z|\big] < 1

@@

or, equivalently,

@@

    \mathbb{E}\big[z^2\big]    & < 1
    \frac{\bar{\Sigma}}{\mu^2} & < 1

@@

@@

\xxx{THIS ALL NEEDS TO BE REWRITTEN!}

\section{Computing $\tilde{\pmb{\Sigma}}$}
%
Since the expectation is a linear operator, we can write Equation~(\ref{eq:SigmaTildeExp})
as
%
\begin{align}
    \tilde{\pmb{\Sigma}}
     & =
    \frac{1}{\mu^2}
    \sum\limits_{n=0}^\infty
    (-1)^n (n + 1)
    \,
    \mathbb{E}\left[
        z^n
        \Bigg(
        \mu^2 \mathbf{J}_K
        +
        \mu \, \mathbf{j}_K\mathbf{u}^\top \mathbf{L}^\top
        +
        \mu \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top
        +
        \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top
        \Bigg)
        \right]
    - \mathbf{J}_K
    \nonumber \\[0.5em]
     & =
    \sum\limits_{n=0}^\infty
    \frac{(-1)^n}{\mu^{2 + n}}
    \,
    \left(
    \mu^2 \mathbf{P}_n
    +
    \mu \, \mathbf{Q}_n
    +
    \mu \, \mathbf{Q}_n^\top
    +
    \mathbf{R}_n
    \right)
    - \mathbf{J}_K
    \quad,
\end{align}
%
where we define the matrices
%
\begin{align}
    \mathbf{P}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{J}_K \right]
    \nonumber                                                                                                                                                                                  \\[0.5em]
    \mathbf{Q}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top \right]
    \nonumber                                                                                                                                                                                  \\[0.5em]
    \mathbf{R}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top \right]
    \quad.
\end{align}
%
In order to compute these matrices,
we will make use of the expression for the
$n^\mathrm{th}$ moment of the standard normal distribution:
%
\begin{align}
    \mathbb{E}\left[ u^n \right] & = g_n
\end{align}
%
for scalar $u \sim \mathcal{N}(0, 1)$, where
%
\begin{align}
    g_n
     & =
    \begin{cases}
        \dfrac{n!}{2^\frac{n}{2} \left(\frac{n}{2}\right)!} & n \, \mathrm{even}
        \\
        0                                                   & n \, \mathrm{odd}
        \quad.
    \end{cases}
\end{align}
%
\citep[e.g.,][]{Winkelbauer2012}.
We can apply this relation to compute expectations
of products of the components of a random standard normal vector $\mathbf{u}$:
%
\begin{align}
    \mathbb{E}\left[u_i \right]                    & = 0
    \\[1em]
    \mathbb{E}\left[u_i u_j\right]                 & = g_2
    \\[1em]
    \mathbb{E}\left[u_i u_j u_k\right]             & = 0
    \\[1em]
    \mathbb{E}\left[u_i u_j u_k u_l\right]         & =
    g_4 \, \delta_{i, j} \delta_{k, l} \, \delta_{i, k}
    +
    g_2^2 \left(
    \delta_{i, j} \, \delta_{k, l} \, \bar{\delta}_{i, k}
    +
    \delta_{i, k} \, \delta_{j, l} \, \bar{\delta}_{i, j}
    +
    \delta_{i, l} \, \delta_{j, k} \, \bar{\delta}_{i, j}
    \right)
    \\[1em]
    \mathbb{E}\left[u_i u_j u_k u_l u_m\right]     & = 0
    \\[1em]
    \mathbb{E}\left[u_i u_j u_k u_l u_m u_n\right] & =
    ...
    \quad,
\end{align}
%
where $\delta$ is the Kronecker delta and $\bar{\delta} \equiv 1 - \delta$.

@@

    \mathbf{P}_0 & = \mathbb{E}\left[ \mathbf{J}_K \right]

@@

                 & = \mathbf{J}_K

@@

since $\mathbf{J}_K$ is constant. Next,

@@

    \mathbf{P}_1 & = \frac{2}{K}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{J}_K \right]

@@

                 & = \frac{2}{K}\left(\mathbf{j}_K^\top \mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \right]\right) \mathbf{J}_K

@@

    \mathbf{P}_2 & = \frac{3}{K^2}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^2 \mathbf{J}_K \right]

@@

                 & = \frac{3}{K^2}\mathbb{E}\left[\left(\mathbf{j}_K^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j}_K \right)  \mathbf{J}_K \right]

@@

                 & = \frac{3}{K^2}\left(\mathbf{j}_K^\top \mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \mathbf{u}^\top \right] \mathbf{L}^\top \, \mathbf{j}_K \right)  \mathbf{J}_K

@@

                 & = \frac{3}{K^2}\left(\mathbf{j}_K^\top \mathbf{L} \mathbf{L}^\top \, \mathbf{j}_K \right)  \mathbf{J}_K

@@

                 & = \frac{3}{K^2}\mathrm{sum}(\mathbf{\Sigma}) \mathbf{J}_K

@@

                 & = 3 \, \bar{\Sigma} \, \mathbf{J}_K

@@

where $\bar{\Sigma}$ is the average of all entries in $\pmb{\Sigma}$ and
we made use of the fact that $\mathbb{E}\left[ \mathbf{u} \mathbf{u}^\top\right] = \mathbf{I}_K$.

@@

    \mathbf{P}_3 & = \frac{4}{K^3}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^3 \mathbf{J}_K \right]

@@

                 & = \frac{4}{K^3}\mathbb{E}\left[\left(\mathbf{j}_K^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j}_K \, \mathbf{j}_K^\top \mathbf{L} \,  \mathbf{u} \right) \mathbf{J}_K \right]

@@

                 & = \frac{4}{K^3}\left(\mathbf{j}_K^\top \mathbf{L} \,  \mathbb{E}\left[\mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{J}_K \mathbf{L} \,  \mathbf{u}\right] \right) \mathbf{J}_K

@@

    \mathbb{E}\left[\mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{J}_K \mathbf{L} \,  \mathbf{u}\right]_{i} = \sum\limits_{k,l}(\mathbf{L}^\top \mathbf{J}_K \mathbf{L})_{kl} u_i u_k u_l = 0

@@

    \mathbf{P}_4 & = \frac{5}{K^4}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)^4 \mathbf{J}_K \right]

@@

                 & = \frac{5}{K^4}\mathbb{E}\left[\left(\mathbf{j}_K^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j}_K \, \mathbf{j}_K^\top \mathbf{L} \,  \mathbf{u} \, \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j}_K \right) \mathbf{J}_K \right]

@@

                 & = \frac{5}{K^4}\left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{E} \, \mathbf{L}^\top \, \mathbf{j}_K \right) \mathbf{J}_K

@@

    \mathbf{A} \equiv \mathbf{L}^\top \, \mathbf{J}_K \, \mathbf{L}

@@

    \sum\limits_{k,l}A_{kl} \mathbb{E}(u_i u_j u_k u_l)

@@

    2 A_{ij} + \sum\limits_k A_{kk}

@@

    2 \, \mathbf{A} + \mathrm{tr}(\mathbf{A}) \mathbf{I}_K

@@

    2 \, \mathbf{L}^\top \, \mathbf{J}_K \, \mathbf{L} + \mathrm{sum}(\pmb{\Sigma}) \mathbf{I}_K

@@

    2 \, \big(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{L}^\top \, \mathbf{J}_K \, \mathbf{L} \, \mathbf{L}^\top \, \mathbf{j}_K \big)

@@

    \mathrm{sum}(\pmb{\Sigma}) \big(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{L}^\top \, \mathbf{j}_K \big)
    \bigg) \mathbf{J}_K

@@

    3 \, \bar{\Sigma}^2 \mathbf{J}_K

@@

        g_n (n + 1) \, \bar{\Sigma}^\frac{n}{2} & n \, \mathrm{even}

@@

    \mathbf{Q}_0 & = \mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top \right]

@@

                 & = \mathbf{L} \, \mathbb{E}\left[  \mathbf{u} \right] \, \mathbf{j}_K^\top

@@

    \mathbf{Q}_1 & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top \right]

@@

                 & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \right] \, \mathbf{j}_K^\top

@@

                 & = \frac{1}{K}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} (\mathbf{u}^\top \mathbf{L}^\top \mathbf{j}_K) \right] \, \mathbf{j}_K^\top

@@

                 & = \frac{1}{K}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \mathbf{u}^\top \mathbf{L}^\top  \right] \, \mathbf{J}_K

@@

                 & = \frac{1}{K}\mathbf{L} \, \mathbb{E}\left[  \mathbf{u} \mathbf{u}^\top   \right]  \, \mathbf{L}^\top \mathbf{J}_K

@@

                 & = \frac{1}{K}\mathbf{L} \, \mathbf{L}^\top \mathbf{J}_K

@@

                 & = \frac{1}{K}\pmb{\Sigma} \, \mathbf{J}_K

@@

where we made liberal use of the fact that $\left(\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}\right)$ is a scalar. Continuing,

@@

    \frac{3}{K^3}\mathbf{e} \, \mathbf{j}_K^\top

@@

    \mathbf{v} \equiv \mathbf{L}^\top \, \mathbf{j}_K

>>>>

Let $\mathbf{x} = \left( x_0 \,\, \cdots \,\, x_{K-1} \right)^\top$
be a $K$-dimensional multivariate normal random variable distributed
according to a Gaussian Process with mean $\pmb{\mu}$
and covariance $\pmb{\Sigma}$:
%
\begin{align}
    \mathbf{x} \sim \mathcal{N}\left( \pmb{\mu}, \pmb{\Sigma} \right)
    \quad.
\end{align}
%
For simplicity, let us assume the mean is constant, i.e.,
%
\begin{align}
    \pmb{\mu} = \mu \, \mathbf{j}
\end{align}
%
where $\mathbf{j}$ is the vector of $K$ ones.
%
Now suppose we cannot observe samples of $\mathbf{x}$ directly, but instead we can
observe samples from the \emph{normalized} process, which we will call
$\tilde{\mathbf{x}}$:
%
\begin{align}
    \tilde{\mathbf{x}}
     & \equiv \frac{\mathbf{x}}{\bar{x}}
    \nonumber                                                    \\[0.5em]
     & = \frac{\mathbf{x}}{\frac{1}{K}\sum\limits_{k=0}^{K-1} x}
    \quad.
\end{align}
%
The random variable $\tilde{\mathbf{x}}$ is no longer normally distributed, but as long as
the variance of $\bar{x}$ is small, we can approximate it as such. Let the mean
and covariance of $\tilde{\mathbf{x}}$ be $\tilde{\pmb{\mu}}$ and $\tilde{\pmb{\Sigma}}$, respectively:
%
\begin{align}
    \tilde{\mathbf{x}} \mathrel{\dot\sim} \mathcal{N}\left( \tilde{\pmb{\mu}}, \tilde{\pmb{\Sigma}} \right)
    \quad.
\end{align}
%
By definition, the mean is unity, i.e,
%
\begin{align}
    \tilde{\pmb{\mu}} = \mathbf{j}
    \quad.
\end{align}
%
What is the expression for $\tilde{\pmb{\Sigma}}$?

@@

        \left(\frac{\mathbf{x}}{\bar{x}} - \mathbf{j}\right)
        \left(\frac{\mathbf{x}}{\bar{x}} - \mathbf{j}\right)^\top

@@

        \frac{\mathbf{x}\,\mathbf{j}^\top}{\bar{x}}

@@

        \frac{\mathbf{j}\,\mathbf{x}^\top}{\bar{x}}

@@

        \mathbf{j} \, \mathbf{j}^\top

@@

        \frac{\mathbf{j}\,\mathbf{x}^\top}{\bar{x}}

@@

@@

    \mathbf{u} \sim \mathcal{N}\left( 0, \mathbf{I} \right)

@@

where $\mathbf{I}$ is the

@@

            (\pmb{\mu} + \mathbf{L} \mathbf{u})\mathbf{j}^\top

@@

            \mathbf{j}(\pmb{\mu} + \mathbf{L} \mathbf{u})^\top

@@

    \mu + \frac{1}{K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}

@@

    z \equiv \frac{1}{\mu K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}

@@

        \frac{z^2 \, \mathbf{j} \, \mathbf{j}^\top}{(1 + z)^2}

@@

        \frac{z\, \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top}{(1 + z)^2}

@@

intractable. Provided
$\big|z| < 1$ (an assumption we'll revisit below), we can Taylor expand the matrices as

@@

        \mathbf{j}^\top

@@

In the Appendix, we show that the expecations in the expressions above may be computed from

@@

        z^{n + 2} \, \mathbf{j} \, \mathbf{j}^\top

@@

    \frac{(n + 1) g_{n} \bar{\sigma}^\frac{n+2}{2}}{\mu^{n+2}} \, \mathbf{j} \, \mathbf{j}^\top

@@

        z^{n + 1} \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top

@@

    \frac{(n + 1) K \, g_{n} \bar{\sigma}^\frac{n}{2}}{\mu^{n+1}} \, \bar{\pmb{\sigma}} \, \mathbf{j}^\top

@@

    \frac{g_n}{\mu^n} \left(
    n \,  \bar{\sigma}^\frac{n - 2}{2} \bar{\pmb{\sigma}} \, \bar{\pmb{\sigma}}^\top + \bar{\sigma}^\frac{n}{2} \pmb{\Sigma}

@@

where

@@

is the expression for the $n^\mathrm{th}$ moment of the standard normal distribution,

@@

    \bar{\pmb{\sigma}}

@@

    \frac{1}{K} \pmb{\Sigma} \, \mathbf{j}

@@

is the average of each row in $\pmb{\Sigma}$, and

@@

    \bar{\sigma}
    \frac{1}{K^2} \mathbf{j}^\top \pmb{\Sigma} \, \mathbf{j}
is the average of all the elements in $\pmb{\Sigma}$.
Inserting these expressions into Equation~(\ref{eq:SigmaPQR}) and rearranging, we obtain

@@

    \frac{\alpha \, \pmb{\Sigma}}{\mu^2}  +
    \frac{\alpha \, \left(\mathbf{s} \, \mathbf{s}^\top - \bar{\pmb{\sigma}} \, \bar{\pmb{\sigma}}^\top\right)}{\mu^2 \bar{\sigma}}  +
    \frac{\beta \, \left(\mathbf{s} \, \mathbf{s}^\top\right)}{\mu^2 \bar{\sigma}}

@@

where

@@

    \mathbf{s}
    \bar{\sigma} \, \mathbf{j} - \bar{\pmb{\sigma}}

@@

@@

    \alpha
    \sum\limits_{n=0}^N
    \frac{(2n + 1)!}{2^n \, n!}
    \frac{\bar{\sigma}}{\mu^2}
    \right)^n
    \beta
    \sum\limits_{n=0}^N
    \frac{2n(2n + 1)!}{2^n \, n!}
    \frac{\bar{\sigma}}{\mu^2}
    \right)^n

@@

This series is divergent!
This may be understood intuitively: given a (very) large number of draws from
a Gaussian process, one of the draws will eventually correspond to a value of
$\mathbf{x}$ whose
mean $\bar{x}$ is arbitrarily close to zero, for which the denominators in the
expectations in Equation~(\ref{eq:SigmaTildeExp}) diverge.

While this is true for any
$\mu$ and $\pmb{\Sigma} \ne \mathbf{0}$, in practice the probability of
drawing $\bar{x} \approx 0$ is vanishingly small provided that
%
\begin{align}
    \frac{\bar{\sigma}}{\mu^2} \ll 1
    \quad.
\end{align}
%
In this limit, any attempt to approximate $\tilde{\pmb{\Sigma}}$
numerically will yield a consistent, finite solution that
asymptotically approaches the expression derived above.

\ifdefined \includeAppendix

@@

    \section{Computing $\tilde{\pmb{\Sigma}}$}
    %
    Since the expectation is a linear operator, we can write Equation~(\ref{eq:SigmaTildeExp})
    as
    %
    \begin{align}
        \tilde{\pmb{\Sigma}}
         & =
        \frac{1}{\mu^2}
        \sum\limits_{n=0}^\infty
        (-1)^n (n + 1)
        \,
        \mathbb{E}\left[
            z^n
            \Bigg(
            \mu^2 \mathbf{j} \, \mathbf{j}^\top
            +
            \mu \, \mathbf{j}\mathbf{u}^\top \mathbf{L}^\top
            +
            \mu \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top
            +
            \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top
            \Bigg)
            \right]
        - \mathbf{j} \, \mathbf{j}^\top
        \nonumber \\[0.5em]
         & =
        \sum\limits_{n=0}^\infty
        \frac{(-1)^n}{\mu^{2 + n}}
        \,
        \left(
        \mu^2 \mathbf{P}_n
        +
        \mu \, \mathbf{Q}_n
        +
        \mu \, \mathbf{Q}_n^\top
        +
        \mathbf{R}_n
        \right)
        - \mathbf{j} \, \mathbf{j}^\top
        \quad,
    \end{align}
    %
    where we define the matrices
    %
    \begin{align}
        \mathbf{P}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{j} \, \mathbf{j}^\top \right]
        \nonumber                                                                                                                                                                                \\[0.5em]
        \mathbf{Q}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top \right]
        \nonumber                                                                                                                                                                                \\[0.5em]
        \mathbf{R}_n & \equiv \frac{(n + 1)}{K^n}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^n \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top \right]
        \quad.
    \end{align}
    %
    In order to compute these matrices,
    we will make use of the expression for the
    $n^\mathrm{th}$ moment of the standard normal distribution:
    %
    \begin{align}
        \mathbb{E}\left[ u^n \right] & = g_n
    \end{align}
    %
    for scalar $u \sim \mathcal{N}(0, 1)$, where
    %
    \begin{align}
        g_n
         & =
        \begin{cases}
            \dfrac{n!}{2^\frac{n}{2} \left(\frac{n}{2}\right)!} & n \, \mathrm{even}
            \\
            0                                                   & n \, \mathrm{odd}
            \quad.
        \end{cases}
    \end{align}
    %
    \citep[e.g.,][]{Winkelbauer2012}.
    We can apply this relation to compute expectations
    of products of the components of a random standard normal vector $\mathbf{u}$:
    %
    \begin{align}
        \mathbb{E}\left[u_i \right]                  & = 0
        \\[1em]
        \mathbb{E}\left[u_i u_j\right]               & = g_2
        \\[1em]
        \mathbb{E}\left[u_i u_j u\right]             & = 0
        \\[1em]
        \mathbb{E}\left[u_i u_j u u_l\right]         & =
        g_4 \, \delta_{i, j} \delta_{k, l} \, \delta_{i, k}
        +
        g_2^2 \left(
        \delta_{i, j} \, \delta_{k, l} \, \bar{\delta}_{i, k}
        +
        \delta_{i, k} \, \delta_{j, l} \, \bar{\delta}_{i, j}
        +
        \delta_{i, l} \, \delta_{j, k} \, \bar{\delta}_{i, j}
        \right)
        \\[1em]
        \mathbb{E}\left[u_i u_j u u_l u_m\right]     & = 0
        \\[1em]
        \mathbb{E}\left[u_i u_j u u_l u_m u_n\right] & =
        ...
        \quad,
    \end{align}
    %
    where $\delta$ is the Kronecker delta and $\bar{\delta} \equiv 1 - \delta$.

@@

        \mathbf{P}_0 & = \mathbb{E}\left[ \mathbf{j} \, \mathbf{j}^\top \right]

@@

                     & = \mathbf{j} \, \mathbf{j}^\top

@@

    since $\mathbf{j} \, \mathbf{j}^\top$ is constant. Next,

@@

        \mathbf{P}_1 & = \frac{2}{K}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{j} \, \mathbf{j}^\top \right]

@@

                     & = \frac{2}{K}\left(\mathbf{j}^\top \mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \right]\right) \mathbf{j} \, \mathbf{j}^\top

@@

        \mathbf{P}_2 & = \frac{3}{K^2}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^2 \mathbf{j} \, \mathbf{j}^\top \right]

@@

                     & = \frac{3}{K^2}\mathbb{E}\left[\left(\mathbf{j}^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \right)  \mathbf{j} \, \mathbf{j}^\top \right]

@@

                     & = \frac{3}{K^2}\left(\mathbf{j}^\top \mathbf{L} \, \mathbb{E}\left[ \mathbf{u} \mathbf{u}^\top \right] \mathbf{L}^\top \, \mathbf{j} \right)  \mathbf{j} \, \mathbf{j}^\top

@@

                     & = \frac{3}{K^2}\left(\mathbf{j}^\top \mathbf{L} \mathbf{L}^\top \, \mathbf{j} \right)  \mathbf{j} \, \mathbf{j}^\top

@@

                     & = \frac{3}{K^2}\mathrm{sum}(\mathbf{\Sigma}) \mathbf{j} \, \mathbf{j}^\top

@@

                     & = 3 \, \bar{\sigma} \, \mathbf{j} \, \mathbf{j}^\top

@@

    where $\bar{\sigma}$ is the average of all entries in $\pmb{\Sigma}$ and
    we made use of the fact that $\mathbb{E}\left[ \mathbf{u} \mathbf{u}^\top\right] = \mathbf{I}$.

@@

        \mathbf{P}_3 & = \frac{4}{K^3}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^3 \mathbf{j} \, \mathbf{j}^\top \right]

@@

                     & = \frac{4}{K^3}\mathbb{E}\left[\left(\mathbf{j}^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \mathbf{L} \,  \mathbf{u} \right) \mathbf{j} \, \mathbf{j}^\top \right]

@@

                     & = \frac{4}{K^3}\left(\mathbf{j}^\top \mathbf{L} \,  \mathbb{E}\left[\mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \mathbf{L} \,  \mathbf{u}\right] \right) \mathbf{j} \, \mathbf{j}^\top

@@

        \mathbb{E}\left[\mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \mathbf{L} \,  \mathbf{u}\right]_{i} = \sum\limits_{k,l}(\mathbf{L}^\top \mathbf{j} \, \mathbf{j}^\top \mathbf{L})_{kl} u_i u u_l = 0

@@

        \mathbf{P}_4 & = \frac{5}{K^4}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^4 \mathbf{j} \, \mathbf{j}^\top \right]

@@

                     & = \frac{5}{K^4}\mathbb{E}\left[\left(\mathbf{j}^\top \mathbf{L} \,  \mathbf{u} \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \mathbf{L} \,  \mathbf{u} \, \mathbf{u}^\top  \mathbf{L}^\top \, \mathbf{j} \right) \mathbf{j} \, \mathbf{j}^\top \right]

@@

                     & = \frac{5}{K^4}\left(\mathbf{j}^\top \mathbf{L} \, \mathbf{E} \, \mathbf{L}^\top \, \mathbf{j} \right) \mathbf{j} \, \mathbf{j}^\top

@@

        \mathbf{A} \equiv \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \, \mathbf{L}

@@

        \sum\limits_{k,l}A_{kl} \mathbb{E}(u_i u_j u u_l)

@@

        2 A_{ij} + \sum\limits A_{kk}

@@

        2 \, \mathbf{A} + \mathrm{tr}(\mathbf{A}) \mathbf{I}

@@

        2 \, \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \, \mathbf{L} + \mathrm{sum}(\pmb{\Sigma}) \mathbf{I}

@@

        2 \, \big(\mathbf{j}^\top \mathbf{L} \, \mathbf{L}^\top \, \mathbf{j} \, \mathbf{j}^\top \, \mathbf{L} \, \mathbf{L}^\top \, \mathbf{j} \big)

@@

        \mathrm{sum}(\pmb{\Sigma}) \big(\mathbf{j}^\top \mathbf{L} \, \mathbf{L}^\top \, \mathbf{j} \big)
        \bigg) \mathbf{j} \, \mathbf{j}^\top

@@

        3 \, \bar{\sigma}^2 \mathbf{j} \, \mathbf{j}^\top

@@

            g_n (n + 1) \, \bar{\sigma}^\frac{n}{2} & n \, \mathrm{even}

@@

        \mathbf{Q}_0 & = \mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top \right]

@@

                     & = \mathbf{L} \, \mathbb{E}\left[  \mathbf{u} \right] \, \mathbf{j}^\top

@@

        \mathbf{Q}_1 & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \, \mathbf{j}^\top \right]

@@

                     & = \frac{1}{K}\mathbb{E}\left[ \left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right) \mathbf{L} \, \mathbf{u} \right] \, \mathbf{j}^\top

@@

                     & = \frac{1}{K}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} (\mathbf{u}^\top \mathbf{L}^\top \mathbf{j}) \right] \, \mathbf{j}^\top

@@

                     & = \frac{1}{K}\mathbb{E}\left[ \mathbf{L} \, \mathbf{u} \mathbf{u}^\top \mathbf{L}^\top  \right] \, \mathbf{j} \, \mathbf{j}^\top

@@

                     & = \frac{1}{K}\mathbf{L} \, \mathbb{E}\left[  \mathbf{u} \mathbf{u}^\top   \right]  \, \mathbf{L}^\top \mathbf{j} \, \mathbf{j}^\top

@@

                     & = \frac{1}{K}\mathbf{L} \, \mathbf{L}^\top \mathbf{j} \, \mathbf{j}^\top

@@

                     & = \frac{1}{K}\pmb{\Sigma} \, \mathbf{j} \, \mathbf{j}^\top

@@

    where we made liberal use of the fact that $\left(\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)$ is a scalar. Continuing,

@@

        \frac{3}{K^3}\mathbf{e} \, \mathbf{j}^\top

@@

        \mathbf{v} \equiv \mathbf{L}^\top \, \mathbf{j}
